|

### 2023-03-28 paper/01-introduction.Rmd
Editing.

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

The first BDB led to several contributions largely focused offensive performance evaluation. For example. finalists @deshpande2020expected introduced an approach for modeling the hypothetical completional probability of a pass aiding in the evalaution of quarterback (QB) decision making. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going]. Since its inception, the BDB has changed themes each year leading to new insight about evaluating different positions such as running backs, defensive backs, and special teams. The [2023 edition of the NFL BDB](https://www.kaggle.com/competitions/nfl-big-data-bowl-2023) continued this revolving theme by asking participants to evaluate lineman on passing plays.

In this work, using data made available in the 2023 BDB, we present a novel approach to measure the performance of pass rushers (defensive players charging the QB). Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.

@@

## Previous Pass Rush Metrics

@@

>>>>

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.

This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.

For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

The first BDB led to several contributions largely focused on offensive performance evaluation. For example, one group of finalists introduced an approach for modeling the hypothetical completion probability of a pass aiding in the evaluation of quarterback (QB) decision making [@deshpande2020expected]. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle (pun intended) a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with Gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going].  Since its inception, the BDB has chosen a different theme each year leading to new insight about evaluating different positions such as running backs, defensive backs, and special teams. The [2023 edition of the NFL BDB](https://www.kaggle.com/competitions/nfl-big-data-bowl-2023) asked participants to evaluate lineman on passing plays [@Howard2023NFL].

In this work, using data made available in the 2023 BDB, we present a novel approach to measure the performance of pass rushers (defensive players whose role on a given play is to put pressure on the QB). Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.

@@

## Previous Pass Rush Metrics
The most widely know metric for tracking pass rusher performance is the sack.  A sack is defined as follows: "to tackle (the quarterback) behind the line of scrimmage before the quarterback is able to throw a pass" (https://www.dictionary.com/browse/sack#:~:text=Football.%20to%20tackle%20(the%20quarterback,Verb%20Phrases) and has been officially tracked in the NFL since 1982 (citation?).  Sacks represent a simple binary measure of success for a rusher on a pass play.  However, there are many intermediate outcomes for a rusher that can also be considered successes that don't result in a sack.  Measures such a hits and hurries are collected by various outlets where hits counts the number of times a QB is hit while passing and hurries counts how often a QB has to throw the ball earlier than they would have liked to.

The sum of sacks, hits, and hurries has been defined as "pressures" (https://www.pro-football-reference.com/years/2022/advanced.htm) and is an improvement over simply sacks, but suffers from problems of subjectivity (i.e. was the play actually a hurry?) and are still binary outcomes (i.e. There is a continuum of plays that aren't hurries that all counted as simply "not hurries")

hurries hits and sacks are "pressures"

@@

Sack definition:
